---
title: "Initial Korean covid 19"
author: "Marina Ornelas"
date: "3/30/23"
output:
  html_document: default
  pdf_document: default
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
options(digits=2)
require(tidyverse)
require(tigerstats)
require(lubridate)
kRdata <- read.csv(file = 'kRdata.csv')
kRdata <- kRdata %>%
mutate(across(where(is.character), as.factor))

```
### Data is from the Patient_Info dataset from South Korea 1 Jan to 1 May 2020
### This data was retrieved from a downloadable zip file from kaggle

Some of the data was uncoded for sex - sex must be just male or female
77 of the data entries were coded sex  as blank, so we omit these.
state of a patient must be died or alive - we adjust that as well   
  
# Your Question - Is dying independent of sex?






## Graphical results - use ggplot commands to do this  
```{r}
barchartGC(~result + Sex, data= kRdata)
barchartGC(~result + Sex,data= kRdata, type="percent")

```

Looking at the bar graph above, we can see that there were more males dying over the amount of females. The percentage for the males alive is lower than the percentage of females alive. Looking at the frequency of the populations, we see that overall females have a higher rate of survival compared to the males rate of survival from this experiment. 

## Numerical results
```{r}
table1 <- xtabs(~result + Sex, data=kRdata)
rowPerc(table1)
colPerc(table1)
```

Looking at the table above, it shows that the results consisted of there being 56% of females alive with 44% of the males being alive. This left us with around 36% of the female populating dying and 64% of the male population dying. 

## Inferential results 
```{r}
chisq.test(table1)
chisqtestGC(table1)
fisher.test(table1)
```



## Conclusions

